---
title: "AssignmentNo.7"
author: "Nitin Khandare"
date: "August 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(VIM)
library(zoo)
library(tidyverse)
library(caret)
cs7 = read.csv("E:/Term 3/Finance Analitics/AssignmentNo7/cs6.csv")

knitr::opts_chunk$set(echo = TRUE)
```

### Problem Statement: The bank manager wants to understand if the average time for decision is the same for the cases where the accounts opened and where the accounts did not open.



### structure of the Data
```{r}
str(cs7)
```


### summary of the Data
```{r}
summary(cs7)
```

### Missing Value treatment
```{r}

colSums(is.na(cs7))

aggr(cs7)

cs7_data = na.omit(cs7)

dim(cs7_data)

```



### find the outlier
```{r}
boxplot(cs7)

```

### Percentage of outlier
```{r}
### percentage of outlier
PerOutier = function(df){
  num=sapply(df, is.numeric)
  NumOut = function(x){
    q1 = quantile(x, 0.25, na.rm = T)
    q2 = quantile(x, 0.50, na.rm = T)
    q3 = quantile(x, 0.75, na.rm = T)
    iqr = q3-q1
    outlier = x[x > q3 + 1.5*iqr | x < q1 - 1.5*iqr]
    percent = (length(outlier) / length(x))*100
return(percent)
  }
  data=sapply(df[,num], NumOut)
   return(as.data.frame(data))
}

PerOutier(cs7)
```



### outlier treatment of Days.for.decision.after.application column
```{r}

quantiles1 <- quantile(cs7_data$Days.for.decision.after.application, probs = c(.25, .75))


range <- 1.5 * IQR(cs7_data$Days.for.decision.after.application)


normal_cs7 <- subset(cs7_data,
cs7_data$Days.for.decision.after.application > (quantiles1[1] - range) & cs7_data$Days.for.decision.after.application < (quantiles1[2] + range))

```



### mean of the Days.for.decision.after.application
```{r}
mean_ds = mean(normal_cs7$Days.for.decision.after.application)

mean_ds
```



### standard deviation of the Days.for.decision.after.application
```{r}
stand_dev_ds = sd(normal_cs7$Days.for.decision.after.application)

stand_dev_ds
```



### Z score using SD and Mean
```{r}
normal_cs7$Z = (normal_cs7$Days.for.decision.after.application - mean_ds)/stand_dev_ds

summary(normal_cs7$Z)

cs7_data1 = normal_cs7[which(normal_cs7$Z < 3), ]
```



### t.test on the sample
```{r}
t.test(normal_cs7$Days.for.decision.after.application~normal_cs7$Account_open_flag)
```

```{r}

```

