---
title: "AssignmentNo.8"
author: "Nitin Khandare"
date: "August 27, 2018"
output: html_document
---

### The dataset contains last 28 transactions made in a savings account along with total amount
? The transaction is both positive and negative(withdrawal and deposits)
? Find out how to predict the closing amount using the last 28 transactions in a saving account

```{r setup, include=FALSE}

cs8 = read.csv("E:/Term 3/Finance Analitics/cs8.csv")
knitr::opts_chunk$set(echo = TRUE)
```


### Structure of the Data
```{r}
str(cs8)
```

### summary of the data
```{r}
summary(cs8)
```


### check the NA values from data
```{r}
colSums(is.na(cs8))
```

### outlier from the data
```{r}
boxplot(cs8)

```
 
#### check the normalize data or not
```{r}

hist(cs8$Transaction1)
hist(cs8$Transaction1)


hist(cs8$Closing.amount)

#### all the columns are in skewness
```

### we can normalize the data For better prediction
```{r}
library(BBmisc)

data_normcs8 = normalize(cs8, method = "range",range = c(0,1))

hist(data_normcs8$Closing.amount)
```

### Data Sampling
```{r}

train = data_normcs8[sample(seq(1,nrow(data_normcs8)),(0.7*nrow(data_normcs8))),]

test = data_normcs8[sample(seq(1,nrow(data_normcs8)),(0.3*nrow(data_normcs8))),]
```

### model Fitting
```{r}
model = lm(Closing.amount~., data = train)


summary(model)
```

#### prediction 
```{r}
pred = predict(model,test)

```

### actuals_predicteds dataframe.
```{r}
actuals_preds <- data.frame(cbind(actuals=cs8test$Closing.amount, predicteds=pred))  # make actuals_predicteds dataframe.
correlation_accuracy <- cor(actuals_preds)  
head(actuals_preds)
```


### Root Mean Square Error
```{r}
rmse <- sqrt(sum((exp(pred) - test$Closing.amount)^2)/length(test$Closing.amount))
c(RMSE = rmse, R2=summary(model)$r.squared)
```


