---
title: "FinanceCaseStudy3"
author: "Nitin Khandare"
date: "August 20, 2018"
output: html_document
---

### A new bank is opening operations. The Business head wants to understand what expected volumes can be for the different clearing methods available from the Electronic Payment Systems - Representative Data (Updated as on February 01, 2017)

```{r setup, include=FALSE}
cs5 = read.csv("E:/Term 3/Finance Analitics/AssignmentNo.5/cs5.csv")
knitr::opts_chunk$set(echo = TRUE)
```


### structure of Data
```{r}
str(cs5)
```

### summary of Data
```{r}
summary(cs5)
```


### remove h value and impute NA values
```{r}

cs5[cs5 == 'h'] <- NA

```

### find NA Values from data
```{r}
colSums(is.na(cs5))

VIM::aggr(cs5)
```


## Omit the NA value from rows
```{r}

df = na.omit(cs5)

```


### Convert All Columns in Numaric type
```{r}

df$RTGSvolume = as.numeric(df$RTGSvolume)

df$NEFTvolume = as.numeric(df$NEFTvolume)

df$CTS.volume = as.numeric(df$CTS.volume)

df$NACH.volume = as.numeric(df$NACH.volume)

str(df)
```

### find the outlier from Data
```{r}
boxplot(cs5)
```

### plotting of different Volumn
```{r}
corrplot::corrplot(cor(df))
```

### t test between CTS.volume and RTGSvolume
```{r}

t.test(df$CTS.volume ~ df$RTGSvolume)

```

## t test between CTS.volume by UPI.volume
```{r}
t.test(df$CTS.volume ~df$UPI.volume)
```

## t test between RTGSvolume by UPI.volume
```{r}
t.test(df$RTGSvolume ~df$UPI.volume)
```

### linear regression model Fitting
```{r}
model = lm(Totalvolume~., data = df)

summary(model)
```
### 
```{r}
pred = predict(model,df)


```

