---
title: "FinanceCaseStudy2"
author: "Nitin Khandare"
date: "August 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
lp = read.csv("E:/Term 3/Finance Analitics/FinanceCaseStudy2/Loan_portfolio.csv")
knitr::opts_chunk$set(echo = TRUE)
```

### Structure of loan Portfolio data
```{r}
str(lp)
```

## Summary of loan Portfolio data
```{r}
summary(lp)
```

### Check the Missing Values
```{r}


colSums(is.na(lp))
```

## Check the percentage of outlier from loan Portfolio data
```{r}

PerOutlier = function(x) {
   num = sapply(x, is.numeric)
  colOut=function(i) {
  q1 = quantile(i, 0.25, na.rm = T)
q2 = quantile(i, 0.5, na.rm = T)
q3 = quantile(i, 0.75, na.rm = T)
iqr = q3 - q1
outlier = i[i > q3 + 1.5*iqr | i < q1 - 1.5*iqr]
perout = (length(outlier) / length(i))*100
return(perout)
    }
   outlierPer=sapply(x[,num],colOut)
   return(as.data.frame(outlierPer))
}
 
PerOutlier(lp)

```


## Two classes frequency in Tenure month column
```{r}
table(lp$Tenure_months)

```

## histogram of loan amount column
```{r}
hist(lp$loan_amnt)
```

## histogram of funded amount column
```{r}
hist(lp$funded_amnt)
```

## mean of loan amount
```{r}

mean(lp$loan_amnt)
```

### mean of funded amount
```{r}
mean(lp$funded_amnt)
```

### correlation on loan Portfolio data
```{r}
corrplot::corrplot(cor(lp))   
```

## density graph for loan amount
```{r}
lm = density(lp$loan_amnt)
plot(lm)
```

## density graph for funded amount
```{r}
a = density(lp$funded_amnt)
plot(a)
```

### Tenure_months is equal to 36. what is the loan amount mean and standard deviation 
```{r}
l_am_data1 = lp %>% filter(Tenure_months == 36) %>% 
                         group_by(Tenure_months) %>% 
                         summarise(mean_l_amt = mean(loan_amnt),sd_l_amt = sd(loan_amnt))

l_am_data1
```


#### Tenure_months is equal to 60. what is the loan amount mean and standard deviation
```{r}
l_am_data2 = lp %>% filter(Tenure_months == 60) %>% 
                         group_by(Tenure_months) %>% 
                         summarise(mean_l_amt = mean(loan_amnt),sd_l_amt = sd(loan_amnt))

l_am_data2
```


### Tenure_months is equal to 36. what is the funded amount mean and standard deviation
```{r}

f_am_data1 = lp %>% filter(Tenure_months == 36) %>% 
                         group_by(Tenure_months) %>% 
                         summarise(mean_f_amt = mean(funded_amnt),sd_f_amt = sd(funded_amnt))

f_am_data1
```

### Tenure_months is equal to 60. what is the funded amount mean and standard deviation
```{r}

f_am_data2 = lp %>% filter(Tenure_months == 60) %>% 
                         group_by(Tenure_months) %>% 
                         summarise(mean_f_amt = mean(funded_amnt),sd_f_amt = sd(funded_amnt))

f_am_data2
```

