---
title: "FinanceCaseStudy3"
author: "Nitin Khandare"
date: "August 21, 2018"
output: html_document
---


### The RBI has created a table to understand the return on portfolio for different credit cards across different banks. This data is tabulated on a monthly basis from Jan 2013 to Nov 2016. The RBI is keen to understand if the different card portfolio of Vijaya Bank is showing similar performance.

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
library(knitr)
cs3 = read.csv("E:/Term 3/Finance Analitics/AssignmentNo.3/cs3.csv")
knitr::opts_chunk$set(echo = TRUE)
```

## structure of a data
```{r}
str(cs3)
```
### Summary of a Data
```{r}
summary(cs3)
```

## check the dimention and names of column
```{r}
dim(cs3)
names(cs3)
```

## check the NA values or missing values
```{r}
colSums(is.na(cs3))
```

### find the percentage outliers
```{r}

PerOutlier = function(x) {
   num = sapply(x, is.numeric)
  colOut=function(i) {
  q1 = quantile(i, 0.25, na.rm = T)
q2 = quantile(i, 0.5, na.rm = T)
q3 = quantile(i, 0.75, na.rm = T)
iqr = q3 - q1
outlier = i[i > q3 + 1.5*iqr | i < q1 - 1.5*iqr]
perout = (length(outlier) / length(i))*100
return(perout)
    }
   outlierPer=sapply(x[,num],colOut)
   return(kable(as.data.frame(outlierPer)))
}
 
PerOutlier(cs3)

```


## t-test on Vijay bank visa and master card
```{r}
t.test(cs3$Vijaya.Bank.Visa.Gold.Credit.Card,
       cs3$Vijaya.Bank.MasterCard.Global.Card)


## here Vijay bank Card showing different Performance because p value is less than 0.05 
## so here we reject the Null hypothesis.
```




### Anova model on Vijay bank Card Data
```{r}

modelaov = aov(cs3$Vijaya.Bank.Visa.Gold.Credit.Card ~
                 cs3$Vijaya.Bank.MasterCard.Classic.Credit.Card +
                 cs3$Vijaya.Bank.MasterCard.Global.Card + 
                 cs3$Vijaya.Bank.VISA.Classic.International.Card, data = cs3)

modelaov
```

### anova on three columns only
```{r}
modelaov1 = aov(cs3$Vijaya.Bank.Visa.Gold.Credit.Card ~
                 cs3$Vijaya.Bank.MasterCard.Classic.Credit.Card +
                 cs3$Vijaya.Bank.MasterCard.Global.Card, data = cs3)

modelaov1
```


### Sample of only Vijay bank Data
```{r}

cs4vj = cs3[,c(1,2,15,17,19,21)]
```

### Structure of vijay bank sample data
```{r}
str(cs4vj)
```

### t-test on Syndicate cards
```{r}
t.test(cs3$Syndicate.Global.Classic.Credit.Card,
       cs3$Syndicate.Global.Gold.Credit.Card)

## here Syndicate bank card showing Same Performance because p value is greater than 0.05 
## so here we accept the Null hypothesis
```

## t-test on HDFS cards
```{r}
t.test(cs3$HDFC.Cooperate.credit.card,cs3$HDFC.Silver.credit.card)
```


