---
title: "IIFL_CaseStudy"
author: "Nitin Khandare"
date: "August 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(caret)
library(corrplot)
library(class)
library(VIM)
library(zoo)
library(BBmisc)


## Read the data
behavior = read.csv("E:/Term 3/Finance Analitics/India infoline/behavior.csv")

demog = read.csv("E:/Term 3/Finance Analitics/India infoline/demog.csv")
df2 = demog

knitr::opts_chunk$set(echo = TRUE)
```

## structure of a behaviour Data
```{r}
str(behavior)
```

### structure of a behaviour Data
```{r}
str(demog)
```


## Summary OF a behaviour data
```{r}
summary(behavior)
```

### summary of a Demog data

```{r}
summary(demog)
```

### Find the missing Values from Data
```{r}
colSums(is.na(behavior))

colSums(is.na(demog))

aggr(behavior)



```

### Missing Value treatment
```{r}

behavior$Credit_Limit = as.numeric(behavior$Credit_Limit)

df1 = na.locf(behavior)

aggr(df1)

colSums(is.na(df1))

```
## Romoved All NA Values
```{r}

### Read the New Imputted Data
New_behav = read.csv("E:/Term 3/Finance Analitics/India infoline/df1_new.csv")


colSums(is.na(New_behav))


#### it Shows Missing Value Column
aggr(New_behav)
```

## finding the outlier from Data
```{r}
boxplot(New_behav)
```


## percentage of outlier in Data
```{r}


PerOutier = function(df){
  num=sapply(df, is.numeric)
  NumOut = function(x){
    q1 = quantile(x, 0.25, na.rm = T)
    q2 = quantile(x, 0.50, na.rm = T)
    q3 = quantile(x, 0.75, na.rm = T)
    iqr = q3-q1
    outlier = x[x > q3 + 1.5*iqr | x < q1 - 1.5*iqr]
    percent = (length(outlier) / length(x))*100
return(percent)
  }
  data=sapply(df[,num], NumOut)
   return(as.data.frame(data))
}

PerOutier(New_behav)
```


### Data Understanding using histogram
```{r}
hist(New_behav$EBIT, col = "red")

hist(New_behav$Footing)

hist(New_behav$Revenue)

hist(New_behav$Interest_income)

hist(New_behav$Cost_of_Fund)

hist(New_behav$Other_income)

hist(New_behav$Operational_Expenses)

hist(New_behav$Credit_Limit)
```

### Now Here we Merge the DataSets Behavior and Demog
```{r}

New_data = merge(New_behav,demog)

colSums(is.na(New_data))

```


### Data Normalization
```{r}

##dummy_obj = dummyVars(~., data = New_data)

##New_DummyVar_Data = data.frame(predict(dummy_obj, newdata = New_data))

Normalz_data = normalize(New_data,method = 'range',range = c(0,1))
```


## Data Plotting
```{r}

#### Product 1 Earnign before interest and Tax
ggplot(Normalz_data,aes(x = Product1,y = EBIT)) + geom_bar(stat = "identity")

### scatter plot between Revenue and EBIT
ggplot(Normalz_data,aes(x = Revenue,y = EBIT)) + geom_point()

##### product 1 Revenue
ggplot(Normalz_data,aes(x = Product1,y = Revenue)) + geom_bar(stat = "identity")


ggplot(Normalz_data,aes(x = Interest_income ,y = EBIT)) + geom_jitter()


ggplot(Normalz_data,aes(x = Footing ,y = EBIT)) + geom_jitter()
```



### hirarchical model Building to take the group of data
```{r}
Normalz_data = normalize(New_data, method = 'range', range = c(0,1))

# model_hr = kmeans(Normalz_data,centers = 3)

######################################################################

hclust_model = hclust(dist(Normalz_data))


### Dendogram of Hierarchical Clusters

plot(hclust_model)

#######################################################################

Normalz_data$cluster = cutree(hclust_model,k = 3)

data_norm_2d = cmdscale(dist(Normalz_data))

data_norm_2d = as.data.frame(data_norm_2d)

data_norm_2d$cluster = as.factor(data_norm$cluster)

ggplot(data_norm_2d,aes(x = V1,y = V2,color = cluster)) + geom_jitter()


```

```{r}
cor_player = cor(t(data_norm %>% head(10) %>% select(-cluster)))
dim(cor_player)
corrplot::corrplot(cor_player, order = 'hclust', addrect = 2)

```

